### 2013-05-15 paper_draft.tex
Added my second affiliation.

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp E. Bayer$^{2}$, 
Helge Rausch$^{3}$,
Fabian Zimmer$^{4}$,
Julia Reda$^{5}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} Applied Bioinformatics Group, School of Agriculture and Food Sciences, The University of Queensland, Australia
\\
\bf{3} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{4} Evolutionary Genomics and Transcriptomics Lab, Department of Genetics, Evolution and Environment, University College London, England
\\
\bf{5} Johannes Gutenberg University Mayence, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - a crowdsourced web resource for personal genomics}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp E. Bayer$^{2,3}$, 
Helge Rausch$^{4}$,
Fabian Zimmer$^{5}$,
Julia Reda$^{6}$
\\
\bf{1} Molecular Ecology Group, Goethe University Frankfurt am Main, Germany
\\
\bf{2} School of Land, Crop and Food Sciences and Australian Centre for Plant Functional Genomics, University of Queensland, Brisbane, Australia
\\
\bf{3} Australian Centre for Plant Functional Genomics, School of Agriculture and Food Sciences, University of Queensland, Brisbane, Australia
\\
\bf{4} Hochschule f\"ur Technik und Wirtschaft Berlin, Germany 
\\
\bf{5} Evolutionary Genomics and Transcriptomics Lab, Department of Genetics, Evolution and Environment, University College London, England
\\
\bf{6} Johannes Gutenberg University Mayence, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}
